Serology Study on Canine Distemper Virus

### 2020-12-07 analysis/paper/paper.Rmd
Initial commit

---
title: "Serology Study on Canine Distemper Virus
in Coyotes in Urban Chicago"
author:
  - Alexandra Schiller:
      email: schil301@umn.edu
      institute: [University of Minnesota]
      correspondence: true
  - Yourfirstname Yourlastname:
      email: fl@another.edu
      institute: [UofA]
      correspondence: false
institute:
  - UofO: University of One Place
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- The actual document text starts here: -->

@@

global <- glmer(CDV.Result ~ Age.Class + (1|Study.Area) +(1|Year),
                family = binomial(link = "logit"), data = D)
summary(global)
or <- exp(fixef(global))
conf <- exp(confint(global))
Anova(global)
r.squaredGLMM(global)

@@

m <- glmer(CDV.Result ~ Age.Class + social.status + Age.Class * social.status + (1|Year)+ (1|Study.Area),
           family = binomial(link="logit"),data = D)
summary(m)
or <- exp(fixef(m))
conf <- exp(confint(m))
Anova(m)
r.squaredGLMM(global)

>>>>

---
title: "Serology Study on Canine Distemper Virus
in Coyotes in Urban Chicago"
author:
  - Alexandra Schiller:
      email: schil301@umn.edu
      institute: [University of Minnesota]
      correspondence: true
  - Yourfirstname Yourlastname:
      email: fl@another.edu
      institute: [UofA]
      correspondence: false
institute:
  - UofO: University of One Place
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---
Add Code to say not to evaluate any of the codes 
<!-- The actual document text starts here: -->

@@

```{r} 
global <- glmer(CDV.Result ~ Age.Class + (1|Study.Area) +(1|Year),
                family = binomial(link = "logit"), data = D)
summary(global)
or <- exp(fixef(global))
conf <- exp(confint(global))
Anova(global)
r.squaredGLMM(global)
```

Results:

@@

```{r}
m <- glmer(CDV.Result ~ Age.Class + social.status + Age.Class * social.status + (1|Year)+ (1|Study.Area),
           family = binomial(link="logit"),data = D)
summary(m)
or <- exp(fixef(m))
conf <- exp(confint(m))
Anova(m)
r.squaredGLMM(global)
```

Results:
